---
title: "STAT 8426 Poster"
author: "Brian Detweiler"
date: "March 31, 2017"
header-includes:
  - \usepackage{color}
  - \usepackage{xcolor}
  - \usepackage{soul}
  - \usepackage{hyperref}
  - \usepackage[vmargin=1in,hmargin=1in]{geometry}
  - \usepackage{booktabs}
  
output: pdf_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

```{r, warning=FALSE, message=FALSE, echo=FALSE, error=FALSE}
library(rstan)
library(rjags)
library(ggplot2)
library(reshape2)
library(dplyr)
source("DBDA2Eprograms/DBDA2E-utilities.R")
```

```{r}
vna <- read.csv('sortedData_0315.csv')
n <- length(vna[,1])
lambda.1 <- (vna %>% filter(SOC_Tine == 'Control' & DIS_Tine == 'Control') %>% count())[[1]] / n
lambda.2 <- (vna %>% filter(SOC_Tine == 'Control' & DIS_Tine == 'Trained') %>% count())[[1]] / n
lambda.3 <- (vna %>% filter(SOC_Tine == 'Trained' & DIS_Tine == 'Control') %>% count())[[1]] / n
lambda.4 <- (vna %>% filter(SOC_Tine == 'Trained' & DIS_Tine == 'Trained') %>% count())[[1]] / n
```


Let's try the zero-inflated model first:

```{r}
inits <- function() {
  lambda1 <- mean(eyesdata$y[1:30]) + rnorm(1, 0, 0.01)
  theta <-  mean(eyesdata$y[31:48]) - lambda1
  sigma2 <- var(eyesdata$y[1:30])
  
  return(list(lambda = c(lambda1, NA), 
              theta = theta, 
              tau = 1/sigma2, 
              pi = c(30, 48 - 30) / 48))
}

inits()

fileName <- "Assignment_11.1"

modelString ="
model {
  for(i in 1 : N ) {
    y[i] ~ dnorm(mu[i], tau)
    mu[i] <- lambda[T[i]]
    T[i] ~ dcat(pi[])
  }

  pi[1:2] ~ ddirch(alpha[])
  theta ~ dnorm(0.0, 1.0E-6)%_%I(0.0, )
  lambda[1] ~ dnorm(0.0, 1.0E-6)
  lambda[2] <- lambda[1] + theta
  tau ~ dgamma(0.001, 0.001)
  sigma <- 1 / sqrt(tau)
}
"

writeLines(modelString, con=fileName)

planes.model.zero.infl = jags.model(file=fileName, 
                                    data=list(y=planes$y,
                                              count=length(planes$y),
                                              x1=planes$x1,
                                              x2=planes$x2,
                                              x3=planes$x3),
                                    n.chains=4)
        
update(planes.model.zero.infl, n.iter=50000)

planes.DIC.zero.infl <- dic.samples(model = planes.model.zero.infl, n.iter = 200000, thin = 50)
planes.DIC.zero.infl

planes.samples.zero.infl <- coda.samples(model = planes.model.zero.infl, 
                                         variable.names = c("y", "beta1", "beta2", "beta3"), 
                                         n.iter = 200000, 
                                         thin = 50)

diagMCMC(planes.samples.zero.infl)

```

Now let's try a non-zero-inflated Poisson regression:

```{r}
fileName <- "Assignment_11.2"

modelString ="
model {

  for (j in 1:count) {
    y[j] ~ dpois(theta[j])
    theta[j] = exp( eta[j] )
    eta[j] = beta1 * x1[j] + beta2 * x2[j] + beta3 * x3[j]
  }

  beta1 ~ dnorm(0, 1.0E-4)
  beta2 ~ dnorm(0, 1.0E-4)
  beta3 ~ dnorm(0, 1.0E-4)

  a4.min.min ~ dpois(exp(beta2 * min(x2)  + beta3 * min(x3)))
  a4.avg.min ~ dpois(exp(beta2 * mean(x2) + beta3 * min(x3)))
  a4.max.min ~ dpois(exp(beta2 * max(x2)  + beta3 * min(x3)))
  a4.min.avg ~ dpois(exp(beta2 * min(x2)  + beta3 * mean(x3)))
  a4.avg.avg ~ dpois(exp(beta2 * mean(x2) + beta3 * mean(x3)))
  a4.max.avg ~ dpois(exp(beta2 * max(x2)  + beta3 * mean(x3)))
  a4.min.max ~ dpois(exp(beta2 * min(x2)  + beta3 * max(x3)))
  a4.avg.max ~ dpois(exp(beta2 * mean(x2) + beta3 * max(x3)))
  a4.max.max ~ dpois(exp(beta2 * max(x2)  + beta3 * max(x3)))

  a6.min.min ~ dpois(exp(beta1 + beta2 * min(x2)  + beta3 * min(x3)))
  a6.avg.min ~ dpois(exp(beta1 + beta2 * mean(x2) + beta3 * min(x3)))
  a6.max.min ~ dpois(exp(beta1 + beta2 * max(x2)  + beta3 * min(x3)))
  a6.min.avg ~ dpois(exp(beta1 + beta2 * min(x2)  + beta3 * mean(x3)))
  a6.avg.avg ~ dpois(exp(beta1 + beta2 * mean(x2) + beta3 * mean(x3)))
  a6.max.avg ~ dpois(exp(beta1 + beta2 * max(x2)  + beta3 * mean(x3)))
  a6.min.max ~ dpois(exp(beta1 + beta2 * min(x2)  + beta3 * max(x3)))
  a6.avg.max ~ dpois(exp(beta1 + beta2 * mean(x2) + beta3 * max(x3)))
  a6.max.max ~ dpois(exp(beta1 + beta2 * max(x2)  + beta3 * max(x3)))
}
"

writeLines(modelString, con=fileName)

planes.model.pois = jags.model(file=fileName, 
                               data=list(y=planes$y,
                                         count=length(planes$y),
                                         x1=planes$x1,
                                         x2=planes$x2,
                                         x3=planes$x3),
                             n.chains=4)

update(planes.model.pois, n.iter=50000)


planes.DIC.pois <- dic.samples(model = planes.model.pois, n.iter = 200000, thin = 50)

planes.DIC.pois

diffdic(planes.DIC.pois, planes.DIC.zero.infl)
```

This seems to have a slightly better fit than the zero-inflated Poisson model.

```{r}
planes.samples.pois <- coda.samples(model = planes.model.pois, 
                                    variable.names = c("beta1", 
                                                       "beta2", 
                                                       "beta3",
                                                       "a4.min.min",
                                                       "a4.avg.min",
                                                       "a4.max.min",
                                                       "a4.min.avg",
                                                       "a4.avg.avg",
                                                       "a4.max.avg",
                                                       "a4.min.max",
                                                       "a4.avg.max",
                                                       "a6.min.min",
                                                       "a6.avg.min",
                                                       "a6.max.min",
                                                       "a6.min.avg",
                                                       "a6.avg.avg",
                                                       "a6.max.avg",
                                                       "a6.min.max",
                                                       "a6.avg.max",
                                                       "a6.max.max"), 
                                    n.iter = 200000, 
                                    thin = 50)

planes.samples.pois.M <- as.matrix(planes.samples.pois[,"beta1"])
```

Our 95% prediction intervals for each situation, A4 or A6 aircraft, with minimal, average, or maximal bomb load, and minimal, average, or maximal crew experience.
```{r}
summary(planes.samples.pois)

planes.df <- as.data.frame(as.matrix(planes.samples.pois))
planes.df <- planes.df %>% select(-beta1, -beta2, -beta3)

planes.df.melt <- melt(planes.df)

ggplot(planes.df.melt, aes(x=variable, y=value)) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "Aircraft.BombLoad.CrewExperience", y = "Damaged Locations")

```

\begin{flushright}
  $\blacksquare$
\end{flushright}

\pagebreak